Computer Science House Constitution

### 2017-02-12 articles.tex
Convert All Indents to Tabs
The majority of the documents were using tabs, so it made sense to
switch to that for a unified format.
Revoke membership of advisors who no longer meet qualifications

\asection{Advisory Membership}
\asubsection{Advisory Membership Qualifications}
Advisory Membership is open to all members of the Rochester Institute of Technology professional, academic, or administrative staff.
\asubsection{Advisory Membership Selection}
The Executive Board may open nominations for Advisory Members.
The candidates then participate in the Advisory Selection Process as defined in \ref{Selection Process for Advisory Members}
\asubsection{Advisory Membership Expectations}
Advisors are encouraged to offer advice and assistance to the House in any capacity the Advisor is able to help.
Advisors are also encouraged to meet the House members and occasionally attend House activities.
\asubsection{Advisory Membership Privileges}
Advisory Members may advise in all issues brought before the House, use Computer Science House facilities, and attend Computer Science House functions.
\asubsection{Advisory Membership Evaluations}
Advisors are not subject to formal evaluations.
\asubsection{Advisory Membership Resignations}
An Advisor may resign by submitting in writing the reason for resignation to the Chairman.
The resignation will be read at the following House Meeting and become effective at that time.
\asubsection{Advisory Membership Term}
Advisory Membership shall last until the member resigns.

>>>>

\asection{Advisory Membership}
\asubsection{Advisory Membership Qualifications}
Advisory Membership is open to all members of the Rochester Institute of Technology professional, academic, or administrative staff.
\asubsection{Advisory Membership Selection}
The Executive Board may open nominations for Advisory Members.
The candidates then participate in the Advisory Selection Process as defined in \ref{Selection Process for Advisory Members}
\asubsection{Advisory Membership Expectations}
Advisors are encouraged to offer advice and assistance to the House in any capacity the Advisor is able to help.
Advisors are also encouraged to meet the House members and occasionally attend House activities.
\asubsection{Advisory Membership Privileges}
Advisory Members may advise in all issues brought before the House, use Computer Science House facilities, and attend Computer Science House functions.
\asubsection{Advisory Membership Evaluations}
Advisors are not subject to formal evaluations.
\asubsection{Advisory Membership Resignations}
An Advisor may resign by submitting in writing the reason for resignation to the Chairman.
The resignation will be read at the following House Meeting and become effective at that time.
\asubsection{Advisory Membership Term}
Advisory Membership shall last until the Advisor no longer meets the qualifications as defined in \ref{Advisory Membership Qualifications} or until the Advisor resigns.
